\documentclass{article}

\usepackage{fullpage,latexsym,picinpar,amsmath,amsfonts}

\input{macros.tex}

\begin{document}

\centerline{\large \bf CS/MATH111 ASSIGNMENT 1}
%\centerline{due }

\vskip 0.3in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
Give the exact and asymptotic formula for the number $f(n)$ of
letters ``A" printed by Algorithm~\textsc{PrintAs} below.
Your solution must consist of the following steps:
%
\begin{description}
\item{(a)} First express $f(n)$ using a summation notation $\sum$.
\item{(b)} Next, give a closed-form formula for $f(n)$.
\item{(c)}  Finally, give the asymptotic value of the
number of A's (using the $\Theta$-notation.)
\end{description}
\noindent
Include justification for each step. 

\smallskip
\noindent
\emph{Note:} If you need any summation formulas for this problem, you are allowed to look them up, and do not need to prove.

\begin{tabbing}
aa \= aa \= aa \= aa \= aa \= aa \= \kill
\textbf{Algorithm} \textsc{PrintAs} $(n: \mbox{\bf integer})$ \\
      \> \textbf{for} $i \leftarrow 1$ \textbf{to} $3n+2$
                         \textbf{do} \\
      \> \> \textbf{for} $j \leftarrow 1$ \textbf{to} $(i+2)^2$ \textbf{do} print(``A")\\
      
aa \= aa \= aa \= aa \= aa \= aa \= \kill
%\textbf{Algorithm} \textsc{PrintAs} $(n: \mbox{\bf integer})$ \\
      \> \textbf{for} $i \leftarrow 1$ \textbf{to} $(3n+2)^2$
                         \textbf{do} \\
      \> \> \textbf{for} $j \leftarrow 1$ \textbf{to} $i+2$ \textbf{do} print(``A")
\end{tabbing}




\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
(a) Use mathematical induction to prove that $3^n \ge n2^n$ for $n\ge 0$. 
(Note: dealing with the base case may require some thought.)

\smallskip
\noindent (b) Consider a sequence defined recursively as
$D_0 = 2$, $D_1 = 5$, and $D_n = 3D_{n-1}+D_{n-2}$ for
$n\ge 2$. Prove that $D_n = O(3.4^n)$ and $D_n = \Omega(3.2^n)$.

\smallskip
\noindent
\emph{Hint:} 
First, prove by induction that $(3.2)^n \le D_n \le 2(3.4)^n$ for all $n\ge 0$.
\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
Give the asymptotic values of the
following functions, using the $\Theta$-notation:
%
\begin{description}
%
\item{(a)} $ (n^3 + 5 n - 10)( 3 n^2 - n)$
\item{(b)} $3 + 2 \sqrt{n} + \dfrac{n}{\log^2 n}$
\item{(c)} $7n^2\log n + 9 n\log^5n + 15n^3$
\item{(d)} $15n^6 + n^2\cdot 2^n + n^3\log n$
\item{(e)} $n^3 \cdot \dfrac{7^n}{6} + n^5 \cdot 4^n$
%
\end{description}
%
Justify your answers.

%(Here, you don't need to give a complete rigorous proof.
%Give only an informal explanation using asymptotic
%relations between the functions $n^c$, $\log n$, and $c^n$.)
\end{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vskip 0.1in
\paragraph{Submission.}
To submit the homework, you need to upload the pdf file to Gradescope.

\paragraph{Reminders.}
Remember that only {\LaTeX} papers are accepted. 


\end{document}

