\documentclass[12pt]{article}
\usepackage{fullpage,latexsym,picinpar,amsmath,amsfonts}
\input{../../../macros.tex}

\begin{document}
\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}
In the RSA, suppose that Bob chooses $p = 3$ and $q = 43$.
(a) Determine three correct values of the
public exponent $e$. Justify briefly their correctness
(at most 20 words.)

\smallskip
We have
$\phi(n) = (p-1)(q-1) = 2\cdot 42 = 84$.
The value of
$e$ should satisfy: $\gcd(e,84)=1$. Possible solutions are e.g.
$e=5$, $e=11$ or $e=13$.


\bigskip
(b) For one of the $e$'s you selected, compute
the secret exponent $d$. Show your work.

\smallskip
For $e=5$, we compute $d = 5^{-1}\pmod{84}$.
Since $84+1 = 5\cdot 17$, we get $d=17$.
\end{problem}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vfill
\eject
\lineacross

\begin{problem}
Grabbits are genetically modified rabbits that live forever and reproduce asexually on a precise schedule: each grabbit gives birth to three grabbits every Wednesday starting two weeks after birth. So if you start with 1 newly born grabbit, after one week you will still only have 1 grabbit. After two weeks you will have 4 grabbits, namely your first grabbit plus its 3 offspring. In general, how many grabbits will you have after $n$ weeks if you start with one newly born grabbit? Set up a recurrence relation for this problem and solve it.


\smallskip
\noindent (a) Let $G_n$ be the number of grabbits after $n$ weeks. Then $G_n$ includes the $G_{n-1}$ grabbits that were alive in week $n-1$ plus the
newly born grabbits. The number of new grabbits is $3G_{n-2}$, because only the grabbits that were around two weeks earlier can have offspring, and each
of them gives birth to $3$ grabbits. So the recurrence relation is:
%
\begin{align*}
G_n &= G_{n-1} + 3G_{n-2}
	\\
G_0 &= 1
	\\
G_1 &= 1
\end{align*}


\smallskip \noindent 
(b) Characteristic polynomial and its roots:
%
\begin{equation*}
x^2 - x - 3 = 0
\end{equation*}
%
so $x_{1,2} = \frac{1\pm \sqrt {13}}{2}$.

\smallskip \noindent 
(c) General form of the solution:
%
\begin{equation*}
\textstyle G_n = \alpha _{1} (\frac{1 + \sqrt {13}}{2})^n + \alpha _{2} (\frac{1 - \sqrt {13}}{2})^n
\end{equation*}


\smallskip \noindent 
(d) Initial condition equations:
%
\begin{align*}
\alpha_1 + \alpha_2 &= 1 \\
\textstyle \alpha_1(\frac{1+\sqrt {13}}{2}) + \alpha_2(\frac{1-\sqrt {13}}{2}) &= 1
\end{align*}
%
and their solution:
%
\begin{equation*}
	\textstyle
\alpha_1 = \frac{1+\sqrt {13}}{2\sqrt{13}} \quad
\alpha_2 = \frac{-1+\sqrt {13}}{2\sqrt{13}}
\end{equation*}


\smallskip \noindent 
(e) Final answer:
The number of grabbits after $n$ weeks is:
%
\begin{align*}
G_n &= \textstyle \frac{1+\sqrt {13}}{2\sqrt{13}} (\frac{1+ \sqrt {13}}{2})^n 
					 + \frac{-1+\sqrt {13}}{2\sqrt{13}} (\frac{1- \sqrt {13}}{2})^n
					 \\
	&= \textstyle \frac{1}{\sqrt{13}} [ (\frac{1+ \sqrt {13}}{2})^{n+1} 
					 -  (\frac{1- \sqrt {13}}{2})^{n+1} ]
\end{align*}

\end{problem}

\end{document}
